---
title: "BIMM 143 Homework 6"
author: "Fangchao He"
date: "4/24/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## **Function that can analyze PDB data**
### **Inputs (Arguments)**

**name**: name of the protein as a PDB 4-digit alphanumerical identifier.

**chainUsed**: chain used in the protein for the plot. Default: "A", chain A.

**eletyUsed**: atom type. Default: "CA", C-alpha.

### **What the function does**

The function plots a  graph of B-factor vs. residue for the chain of protein specified in PDB. Input the arguments above and run the function to obtain the graph.

### **Output**
returns nothing

plots a graph of B-factor versus residue

### **Code**
```{r}
# Load the package
library(bio3d)

# Function starts here
plot_B_factor <- function(name, chainUsed = "A", eletyUsed = "CA") {
  s <- read.pdb(name)
  new <- trim.pdb(s, chain = chainUsed, elety = eletyUsed)
  plotb3(new$atom$b, sse = new, typ = "l", ylab = "Bfactor")
}
# Function ends
```